\chapter*{Abstract}
\addcontentsline{toc}{chapter}{Abstract}

This report explains MSc students' summer term project - the design and development of Tourlingo, a Multilingual Virtual Tour Assistant web application created in collaboration with Al Fateh Technologies. The webapp Tourlingo is developed to help tourists travel unfamiliar cities with confidence by using real-time translation, cultural insights, and a customised navigation.

The key features include an interactive OpenStreetMap-based map highlighting major points of interest, automatic translation of place names and directions through LibreTranslate, and AI-powered cultural tips tailored to the user’s chosen language. The application is designed to work seamlessly on both desktop and mobile, making it accessible to a wide range of users.

The system was developed by a team of eight MSc Computer Science students using agile practices. Throughout the project, the main challenges were integrating multilingual content, creating an intuitive interface, and ensuring consistent performance across different environments. These were tackled through iterative prototyping, regular client feedback, and extensive user testing, including two dedicated “testathon” events.

The final product demonstrates how open-source mapping, translation, and AI tools can be combined into a scalable and flexible solution. Looking ahead, there is strong potential for future improvements such as expanding language support, integrating premium translation APIs, and enriching the cultural datasets.
